Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-21 paper/paper.tex
Add Ewa's changes to 5.4

We ran simulations for constraint values ranging between the estimated 
limits indicated in Section~\ref{sec:scenarios}, resulting in approximately 
50-150 (budget, deadline) data points for each application. The runs were
repeated for Pareto-distributed and constant workflow ensembles. From this result
space we selected the most interesting plots that characterize the observed 
behavior of the algorithms best.

\begin{figure*}[htb] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Effective computing cost in \$ per hour calculated by dividing sum of
task runtimes by the total budget. Higher cost results from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows.}
\label{fig:cost}
\end{figure*}

Fig.~\ref{fig:number-complete-pareto} shows the number of the workflows
completed for two budget values for each application ensemble. The budget values
selected correspond to two opposite cases: {\em small budget} (top) and {\em
large budget} (bottom). The small budgets permit the algorithms to complete 
only a small number of workflows from the ensemble, while the larger budgets 
enables the algorithms to finish almost all the workflows. In three of five 
cases the SPSS algorithm performs better for tighter constraints: when the 
budget is low, or the deadline is short, the static procedure is able to more 
efficiently pack workflow tasks onto limited resources. This is the case for 
the LIGO, Epigenomics and SIPHT ensembles for small budgets, and for large
budgets with short deadlines. The exceptions are the Montage and CyberShake 
ensembles,  which consist of many fine-grained tasks. In these applications, 
as well for the other ensembles with large budgets and deadlines, the simple 
dynamic scheduling techniques perform equally well or better. For these 
applications the large number of small tasks guarantees that resources 
are almost never idle regardless of how the tasks are scheduled. We also 
observe that WA-DPDS performs better than the workflow-unaware version, DPDS. 
This means that for the tested workflows the simple admission procedure based 
on estimation of workflow cost does not degrade the solution, but rather in 
many cases it enables larger workflows that would lead to budget overrun to
be rejected. Thus it can save the space for smaller workflows to complete.

@@

Fig.~\ref{fig:total-time} presents the same results using the total computing
time metric, $T_C$. These plots confirm our previous observations about the
algorithms' performance, but they also allow us observe a more general property:
for a given budget, when the deadline is tightened the amount of work done
steeply decreases. Assigning a shorter deadline means that more VMs need to be
provisioned to complete the work, but this leads to higher parallelism and thus
to lower parallel efficiency. For example, running 2 VMs for 10 hours will tend
to be more efficient than running 10 VMs for 2 hours. Similarly, the only way 
to reduce cost when adding VMs is to achieve a super-linear speedup, which 
is unlikely in practice. Therefore, if the deadline permits, and cost is 
important, parallelism should be avoided when possible.

>>>>

We ran simulations for constraint values ranging between the estimated 
limits indicated in Section~\ref{sec:scenarios}, resulting in approximately 
50-150 (budget, deadline) data points for each application. The runs were
performed for Pareto-distributed and constant workflow ensembles. From this result
space we selected representative plots.

\begin{figure*}[htb] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Effective computing cost in \$ per hour calculated by dividing the sum of
task runtimes by the total budget. Higher costs result from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows.}
\label{fig:cost}
\end{figure*}

Fig.~\ref{fig:number-complete-pareto} shows the number of the workflows
completed for two budget values for each application ensemble. The budget values
selected correspond to two extreme cases: {\em small budget} (top) and {\em
large budget} (bottom). The small budgets permit the algorithms to complete 
only a small number of workflows from the ensemble, while the larger budgets 
enable the algorithms to finish almost all the workflows. In three of five 
cases the SPSS algorithm performs better for tighter constraints. When the 
budget is low, or the deadline is short, the static procedure is able to more 
efficiently pack workflow tasks onto limited resources. This is the case for 
the LIGO, Epigenomics and SIPHT ensembles for small budgets, and for large
budgets with short deadlines. The exceptions are the Montage and CyberShake 
ensembles,  which consist of many fine-grained tasks. In these applications, 
as well for the other ensembles with large budgets and deadlines, the simple 
dynamic scheduling techniques perform equally well or better. The reason for 
this behavior is that the large number of tasks guarantees that resources 
are almost never idle regardless of how the tasks are scheduled. We also 
observe that WA-DPDS performs better than the workflow-unaware version, DPDS. 
This means that for the workflows we tested the simple admission procedure based 
on estimation of workflow cost does not degrade the solution, but rather in 
many cases it enables larger workflows that would lead to budget overrun to
be rejected. Thus it can save the space for smaller workflows to complete.

@@

Fig.~\ref{fig:total-time} presents the same results using the total computing
time metric, $T_C$. These plots confirm our previous observations about the
algorithms' performance, but they also allow us observe a more general property:
for a given budget, when the deadline is tightened the amount of work done
steeply decreases. Assigning a shorter deadline means that more VMs need to be
provisioned to complete the work. However, because of the dependencies in the 
workflows, many VMs will either be idle, or will be backfilled with tasks from 
low-priority workflows that never finish, resulting in reduced resource 
utilization. Similarly, the only way to reduce cost when adding VMs is to 
achieve a super-linear speedup, which is unlikely in practice. Therefore, if 
the deadline permits, and cost is important, parallelism should be kept to a 
minimum.
